
\documentclass{acmtog} 

\usepackage{german} 
\usepackage[colorlinks=true, urlcolor=blue, linkcolor=blue, citecolor=black]{hyperref}


\acmVolume{1}
\acmNumber{1}
\acmYear{2015}
\acmMonth{1}
\acmArticleNum{}
\acmdoi{}

\begin{document}

\title{Biometrics and Security\\ Speaker Recognition} 

\author{Jonas Marquardt {\upshape und} Maik Riestock
\affil{Otto von Guericke University Magdeburg - Advanced Multimedia and Secruity Lab (AMSL)}}


\keywords{Speaker Recognition, Audio Feature Extraction, Doddingtons Zoo}


\maketitle

\begin{bottomstuff}
This report was created in the context of the course “Biometrics and Security [BIOSEC]” winter term 2014/15.
This course was held by: Prof. Dr.-Ing. Jana Dittmann and Prof. Dr.-Ing. Claus Vielhauer; Research group Multimedia and Security, Otto-von-Guericke-University of Magdeburg, Germany.
The course was supported by: Dr.-Ing. Christian Krätzer, M.Sc. Kun Qian
\end{bottomstuff}


\begin{abstract}
speaker reco\\
orientiert am hyke(database)\\
\textit{Closed set speaker authentication}\\
projektion auf 'Doddingtons Zoo'\\

\end{abstract}

\input{chapters/1-motivation} 		% Jonas
\input{chapters/2-hyke}				% Maik
\input{chapters/3-approach}			% Maik
\input{chapters/4-database}			% Jonas
\input{chapters/5-pre}				% Maik
\input{chapters/6-extraction}		% Jonas
\input{chapters/7-post}				% Jonas
\input{chapters/8-classification}	% Maik
\input{chapters/9-zoo}				% Maik
\input{chapters/10-conclusion}		% Jonas
\input{chapters/11-future}			% Maik

%--------------------------------------------------------------------------------------
\newpage
\input{chapters/sources}
\listoftables
\appendix
\input{chapters/task_describtion}




\end{document}

